### 2021-04-20 paper/ase21/eval.tex
[ASE21] Till Conclusion
[ASE21] Updated Figure 6 and 8
[ASE21] Updated figures and tables in eval

\begin{table*}
  \centering
  \caption{The analysis precision of $\tool$ without refinement
  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
  difference ($\Delta$)}
  \label{table:precision}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{c|c?c|c?c|c?c|c}
    \multirow{2}{*}{\textbf{Checker}} &
    \multirow{2}{*}{\textbf{Bug Kind}} &
    \multicolumn{6}{c}{
      \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
    }\\\cline{3-8} &&
    \multicolumn{2}{c?}{no-refine} &
    \multicolumn{2}{c?}{refine} &
    \multicolumn{2}{c}{$\Delta$}\\

    \myrowc{2}
    {Reference}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
    {UnknownVar}    {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
    \myrowh
    {DuplicatedVar} {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}

    \myrowc{1}
    {Arity}         {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
    {MissParam}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}

    \myrowc{1}
    {Assertion}     {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
    {Assertion}     {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}

    \myrowc{2}
    {Operand}       {60 / 116 (51.7\%)} {60 / 116 (51.7\%)} {\md{12}{3}{51.7}}
    {NoNumber}      {17 / 72 (23.6\%)}  {17 / 72 (23.6\%)}  {\md{12}{3}{51.7}}
    \myrowh
    {Abrupt}        {43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}

    \mysrowh
    {\textbf{Total}}{43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}

@@

\begin{table}
  \centering
  \caption{The creators and resolvers of true bugs.}
  \label{table:author}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{c|c|c?c|c|c}
    \multicolumn{3}{c?}{\textbf{Creator}} &
    \multicolumn{3}{c}{\textbf{Resolver}}\\\hline

    \textbf{Committee} &
    \textbf{Outsider} &
    \textbf{Inherited} &
    \textbf{Committee} &
    \textbf{Outsider} &
    \textbf{NotYet}\\\hline

    \inred{60} &
    \inred{12} &
    \inred{20} &
    \inred{60} &
    \inred{23} &
    \inred{10}\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table}

@@

@@

Moreover, we extended $\tool$ to automatically extract more statistics of
detected true bugs.  \inred{First, we checked that true bugs are created or
resolved by whom as described in Table~\ref{table:author}.  Among \inred{89}
true bugs, we cannot automatically know who created \inred{20}
\textit{inherited} bugs, which are created before 2018.  For remaining
\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
outside contributors not committee members.  On the other hand, most of them
(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
are resolved by non-committee contributors.  Other \inred{14} bugs are newly
found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
statistic of true bugs is Time to Live (TTL) that denotes how many days
specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
histogram of TTLs in a logarithmic scale.  The average days of TTL is
\inred{300.0} even though we assume that \inred{20} inherited bugs are created
in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
corresponding bug is inherited and not yet resolved in the latest version.  We
manually investigated its creation time in the history of the official
repository, and we discovered that it was created at the initial commit of the
open development process in September 22, 2015.  It means that the bug actually
existed for \inred{3,000} days.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-iter}
    \caption{The histogram of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-iter}
    \caption{The ratio of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-time}
    \caption{The histogram of analysis time.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-time}
    \caption{The ratio of analysis time.}
  \end{subfigure}
  \caption{The comparison of iterations and analysis time without refinement
  (\stextsf{no-refine}) and with refinement (\stextsf{refine}).}
  \label{fig:performance-compare}
  \vspace*{-1.5em}
\end{figure}

@@

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{23.2}\% to \inred{23.3}\% by removing \inred{10} false
bugs and to detect \inred{10} more true bugs.  (\todo: investigate the result for
each checker.)

>>>>

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{img/author}
  \caption{The creators and resolvers of true bugs.}
  \label{fig:author}
  \vspace*{-1.5em}
\end{figure}

@@

\begin{table*}
  \centering
  \caption{The analysis precision of $\tool$ without refinement
  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
  difference ($\Delta$)}
  \label{table:precision}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{c|c?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l}
      \multirow{2}{*}{\textbf{Checker}} &
      \multirow{2}{*}{\textbf{Bug Kind}} &
      \multicolumn{24}{c}{
        \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
      }\\\cline{3-26} &&
      \multicolumn{8}{c?}{no-refine} &
      \multicolumn{8}{c?}{refine} &
      \multicolumn{8}{c}{$\Delta$}\\

      \myrowc
      {\mr{2}{\stextsf{Reference}}}
      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
      {\mr{1}{\stextsf{UnknownVar}}}
      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{-}{-28}{+11.1}}

      \myrowh
      {\mr{1}{\stextsf{DuplicatedVar}}}
      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}

      \smyrowc
      {\mr{1}{\stextsf{Arity}}}
      {\mr{1}{\stextsf{MissParam}}}
      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}

      \smyrowc
      {\mr{1}{\stextsf{Assertion}}}
      {\mr{1}{\stextsf{Assertion}}}
      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{-}{-26}{+7.4}}

      \myrowc
      {\mr{2}{\stextsf{Operand}}}
      {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{-}{-69}{+30.5}}
      {\mr{1}{\stextsf{NoNumber}}}
      {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{-}{-59}{+30.3}}

      \myrowh
      {\mr{1}{\stextsf{Abrupt}}}
      {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{-}{-10}{+11.0}}

      \mysrowh
      {\textbf{Total}}
      {91 / 299 (30.4\%)}{92 / 177 (52.0\%)}{+1 / -122 (+21.5\%)}

@@

Moreover, we extended $\tool$ to automatically extract more statistics of
detected true bugs.  \inred{First, we checked that true bugs are created or
resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{89}
true bugs, we cannot automatically know who created \inred{20}
\textit{inherited} bugs, which are created before 2018.  For remaining
\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
outside contributors not committee members.  On the other hand, most of them
(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
are resolved by non-committee contributors.  Other \inred{14} bugs are newly
found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
statistic of true bugs is Time to Live (TTL) that denotes how many days
specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
histogram of TTLs in a logarithmic scale.  The average days of TTL is
\inred{300.0} even though we assume that \inred{20} inherited bugs are created
in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
corresponding bug is inherited and not yet resolved in the latest version.  We
manually investigated its creation time in the history of the official
repository, and we discovered that it was created at the initial commit of the
open development process in September 22, 2015.  It means that the bug actually
existed for \inred{3,000} days.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-iter}
    \caption{The histogram of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-iter}
    \caption{The ratio of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-time}
    \caption{The histogram of time.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-time}
    \caption{The ratio of time.}
  \end{subfigure}
  \caption{The comparison of iterations and analysis time without refinement
  (\stextsf{no-refine}) and with refinement (\stextsf{refine}).}
  \label{fig:performance-compare}
  \vspace*{-1.5em}
\end{figure}

@@

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{23.2}\% to \inred{23.3}\% by removing \inred{10} false
bugs and to detect \inred{10} more true bugs.  \inred{(\todo: investigate the result for
each checker.)}
